Supplementary material for ``An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects in Time-Frequency Representations''

### 2020-07-28 Notes/BoundEffRed.tex
new results + paper

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{PPGsig.eps}
\includegraphics[width=.24\textwidth]{zoomSSTintro.eps}
\includegraphics[width=.24\textwidth]{zoomSSTBoundEffRed.eps}
\caption{A segment of PPG signal (top) and the right boundary of a TF representation determined by the SST without extension (bottom left), and the right boundary of a TF representation determined by the SST with the proposed boundary effect reduction algorithm by forecasting (bottom right). The window length for the SST is 12~seconds.}
\label{fig:ex.intro}
\end{figure}

Attempts to minimize the boundary effects generally consists in softening the discontinuity on signal edges. For instance, judicious choices of analysis windows whose support does not interfere with the boundary points can minimize the occurrence of aberrant patterns near the boundaries of the TF plane~\cite{Chui92wavelets,Depczynski99fast}. Due to the specific relationship of chosen analysis windows and TF analysis tool, these techniques do not make it possible to reduce the boundary effects of any TF representations, and for any analysis window. Another natural idea consists of carrying out a preliminary step of extending the signal beyond its boundaries, and due to its flexibility, various extension schemes have been proposed. For example, there exist simple extension schemes that do not take into account the dynamical behavior of the signal, such as zero-padding, periodic extension, symmetric extension~\cite{Kharitonenko02wavelet,Chen95symmetric}, or polynomial extrapolation~\cite{Williams97discrete}. There also exist extension schemes based on physically relevant dynamical models, such as the Extended Dynamic Mode Decomposition~\cite{Williams15data} (EDMD), the Gaussian process regression~\cite{Rasmussen06gaussian,Roberts13Gaussian} (GPR), the Trigonometric, Box-Cox transformation, ARMA errors, Trend and Seasonal components (TBATS) algorithm~\cite{DeLivera11forecasting}, the dynamic linear models \cite{west2006bayesian}, and long short-term memory model \cite{vlachas2018data}. It is far from an exhaustive list, and we refer readers with interest to \cite{hyndman2018forecasting} for a friendly monograph on the general forecasting topic. Whereas the second class of extension schemes gives better-extended signals than the first class, they generally have a great computational cost.

In this paper, we propose a fast extension algorithm based on a simple dynamical model, in order to optimize the trade-off between the extension quality and the computational cost. The proposed algorithm is then composed of two steps.
\begin{enumerate}
\item \emph{Extend the signal by forecasting it.} The aim is to use a dynamic model to predict the values taken by the measured signal outside the measurement interval. Then, once this operation is done, we have access to an extended signal defined on a larger interval $I_\Delta$, where $\Delta$ denotes the size of the extension on both boundaries of $I$.
\item \emph{Run the local analysis tool on the extended signal.} Assuming that the support of the analysis window is smaller than $2\Delta$, the local analysis near the boundary of $I$ is now possible without lack of information thanks to knowledge brought by the extension. 
\end{enumerate}
Thus, assuming that the quality of the extension step is sufficient, the analysis results obtained that way will be less sensitive to the boundary effects than the result of the analysis tool applied directly to the nonextended signal. We claim and prove that forecasting oscillatory signals based on the simple dynamical model combined with the simple least square approach is sufficient for reducing the boundary effects for the TF analysis, or other kernel-based analysis. See the bottom right of Fig.~\ref{fig:ex.intro} for a snapshot of the result. The main benefit of this simple approach is a numerically efficient solution with a theoretical guarantee for real-time analysis purposes.

>>>>

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{PPGsig.eps}
%\includegraphics[width=.24\textwidth]{zoomSSTintro.eps}
%\includegraphics[width=.24\textwidth]{zoomSSTBoundEffRed.eps}
\caption{A segment of PPG signal (top) and the right boundary of a TF representation determined by the SST without extension (bottom left), and the right boundary of a TF representation determined by the SST with the proposed boundary effect reduction algorithm by forecasting (bottom right). The window length for the SST is 12~seconds.}
\label{fig:ex.intro}
\end{figure}

Attempts to minimize the boundary effects generally consists in softening the discontinuity on signal edges. Usually the approaches can be classified into two main classes, choosing a proper analysis window and extending/forecasting the signal. In the first class, judicious choice of analysis window whose support does not interfere with the boundary points can minimize the occurrence of aberrant patterns near the boundaries of the TF plane, for instance, \cite{Chui92wavelets,Depczynski99fast}. Due to the specific relationship of chosen analysis windows and TF analysis tool, these techniques do not make it possible to reduce the boundary effects of any TF representations. 
%
Another natural idea, the second class, consists of carrying out a preliminary step of extending, or forecasting, the signal beyond its boundaries. Due to its flexibility, various forecasting schemes have been proposed. For example, there exist simple extension schemes that do not take into account the dynamical behavior of the signal, such as zero-padding, periodic extension, symmetric extension~\cite{Kharitonenko02wavelet,Chen95symmetric}, or polynomial extrapolation~\cite{Williams97discrete}. 
%
There exist extension schemes based on physically relevant dynamical models, such as the Extended Dynamic Mode Decomposition~\cite{Williams15data} (EDMD) and the Gaussian process regression~\cite{Rasmussen06gaussian,Roberts13Gaussian} (GPR). There also exist extension schemes based on stochastic models, such as the Trigonometric, Box-Cox transformation, ARMA errors, Trend and Seasonal components (TBATS) algorithm~\cite{DeLivera11forecasting}, the dynamic linear models \cite{west2006bayesian}. 
%
In the physically relevant dynamical models, the oscillation or trend, are usually modeled as the mean of a stochastic process, while in the stochastic models, the oscillation or trend are modeled by the covariance structure of the stochastic process. 
It is also possible to consider polynomial regression \cite{fan1996local} or modeling the mean by splines \cite{hall2005theory}, kernel functions \cite{chang2010training}, and wavelets \cite{marron1998exact}, or nonparametric regression \cite{fan1996local}, to estimate the mean function and hence forecasting the signal. Neural network models, such as the long short-term memory model \cite{vlachas2018data}, is another approach. 
%
The above is a far from exhaustive list, and we refer readers with interest to \cite{hyndman2018forecasting} for a friendly monograph on the general forecasting topic. 
%
While the model-based extension scheme gives better-extended signals than those simple extension without dynamical models, they generally have a great computational cost.

In this paper, we propose a fast extension algorithm based on a simple dynamical model that optimizes the trade-off between the extension quality and the computational cost, so that the real-time analysis can be achieved. The algorithm is composed of two steps.
\begin{enumerate}
\item \emph{Extend the signal by forecasting it.} The aim is to use a simple dynamic model to predict the values taken by the measured signal outside the measurement interval. Then, once this operation is done, we have access to an extended signal defined on a larger interval $I_\Delta$, where $\Delta$ denotes the size of the extension on both boundaries of $I$.
\item \emph{Run the local analysis tool on the extended signal.} Assuming that the support of the analysis window is smaller than $2\Delta$, the local analysis near the boundary of $I$ is now possible without lack of information thanks to knowledge brought by the extension. 
\end{enumerate}

Thus, assuming that the quality of the extension step is sufficient, the analysis results obtained that way will be less sensitive to the boundary effects than the result of the analysis tool applied directly to the nonextended signal. We claim and prove that forecasting oscillatory signals based on the simple dynamical model combined with the simple least square approach is sufficient for reducing the boundary effects for the TF analysis, or other kernel-based analysis. See the bottom right of Fig.~\ref{fig:ex.intro} for a snapshot of the result. The main benefit of this simple approach is a numerically efficient solution with a theoretical guarantee for real-time analysis purposes.

### 2020-07-28 Notes/Supplementary material/SupMat.tex
new results + paper

\title{An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects\\ in Time-Frequency Representations:\\ Part II}

@@

\subsection{Notations}
By definition the matrix $\bX$ and $\bY$ and because of the noisy signal model~\eqref{I-eq:model.noise}, we have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} = \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$, with:
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.

\begin{remark}
The matrices $\bE^{(0)}$ and $\bE^{(1)}$ are said to be error matrices because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
\end{remark}

It follows from this:
\begin{align*}
\tilde\bA &= (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv \\
\bA_0 &=\bS^{(1)}{\bS^{(0)}}^\inv\ .
\end{align*}
Then:
\begin{align}
\nonumber
\bh^{(\ell)} &= \balpha^{(\ell)} - \balpha^{(\ell)}_0 \\
\nonumber
&= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

\subsection{Study of $\bh^{(\ell)}$}
The randomness of $\bh^{(\ell)}$ is completely originating from the error matrices. Besides, notice that the first $M-1$ rows in $\bE^{(1)}$ are equals to the last $M-1$ rows of $\bE^{(0)}$. Thus, we gather all the sources of randomness into an vector $\bg\in\RR^{M(M+1)}$, containing $M$ rows and defined as:
\[
\bg = \vec\left(
\begin{pmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{pmatrix}
\right)\ .
\]
Here, "$\vec$" denotes the vectorization operator, concatenating the columns of a given matrix on top of one another. Then, by definition, we have:
\[
\bg = \sigma\bg_1 + \sigma^2\bg_2\ ,
\]
where:
\begin{align*}
\bg_1 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left( \tilde\bz_k\bw_k^T + \tilde\bw_k\bz_k^T \right) \\
\bg_2 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left(\tilde\bw_k\bw_k^T-\tilde\bI \right) \ .
\end{align*}
with $\tilde\bz_k^T= \begin{pmatrix} \bz_k^T & \bz_{k+1}[M-1] \end{pmatrix}$ and $\tilde\bw_k^T= \begin{pmatrix} \bw_k^T & \bw_{k+1}[M-1] \end{pmatrix}$. Then, $\bg_1$ is a Gaussian random vector because it is a linear combination of Gaussian random vectors. Moreover, using the central limit theorem under weak dependence, we can show that $\bg_2$ also converges towards a Gaussian random vector as $K\to\infty$. Combining these two results gives the following result:
\[
\sqrt{K}\ \bg \xrightarrow[K\to\infty]{\cD} \cN(\bzero,\bGamma_0)\ ,
\]
where $\bGamma_0=\EE\left\{\bg\bg^T\right\}$ is a covariance matrix.

Furthermore, one can write $\bh^{(\ell)}$ as $\bh^{(\ell)}=f^{(\ell)}(\bg)$ where $f^{(\ell)}$ is a deterministic function such that:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ . \\
\end{align*}
Then, as $f^{(\ell)}$ is a differentiable function, using the Delta method gives:
\begin{align*}
\sqrt{K}\ \bh^{(\ell)} \xrightarrow[K\to\infty]{\cD} \cN(\bzero,{\bF^{(\ell)}}^T\bGamma_0\bF^{(\ell)})\ ,
\end{align*}
where $\bF^{(\ell)}$ is the Jacobian matrix such that:
\[
\bF^{(\ell)}[m,m'] = \left.\dfrac{\partial f^{(\ell)}_m}{\partial\bg[m']}\right\vert_{\bg=\bzero}\ .
\]

@@

\subsection{Expression of the Bias $\bmu$.}
Clearly, $\bmu[n]=0$ when $n\in I$. When $n=N-1+\ell$, we have:

@@

Let us first evaluate the expression of $\balpha_0^{(\ell)}\bz_K$. We have:

@@

where $\bU[m,m']=\frac1{\sqrt{M}}e^{-2\ii\pi mm'/M}$ and $\bLambda^{(0)} = \mathrm{diag}(\lambda_0^{(0)},\dots,\lambda_{M-1}^{(0)})$ with:

@@

Therefore:

@@

{\bS^{(0)}}^\inv  &= \bU{\bLambda^{(0)}}^\inv\bU^*

@@

which leads to:

@@

{\bS^{(0)}}^\inv[m,m']  &= \dfrac1{\sigma^2}\delta_{m,m'}-\sum_{j=1}^J\dfrac{\Omega_j^2}{2\sigma^2(\sigma^2+\Omega_j^2M/4)}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\ ,

@@

and, consequently:

@@

&= \delta_{m+1,m'} + \sum_{j=1}^J\dfrac{2\Omega_j^2}{\Omega_j^2M+4\sigma^2}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}

@@

Thus:

@@

@@

By induction, we have:

@@

\ .

@@

Then:

@@

&=\sum_{m=0}^{M-\ell}\balpha_0^{(1)}[m]\bz[N-M+\ell+m-1]+\sum_{m=M-\ell+1}^{M-1}\balpha_0^{(1)}[m]\balpha_0^{(m-M+\ell)}\bz_K

@@

But:

@@

and, by induction from~\eqref{eq:seq}:

@@

Consequently:

@@

\bmu[N-1+\ell] \underset{K\to\infty}{\sim} o(\sigma)\ .

@@

\subsection{Expression of the Covariance $\bgamma$.}
We recall that $n>N$, we consequently denote $n=N-1+\ell$.  To derive the covariance, let us segregate the cases.

\paragraph{If $n'\in I^2$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing. Then, combining result~\eqref{eq:bias.ap} and equation~\eqref{I-eq:bias0}, we obtain:
\begin{align*}
\bgamma[n,n'] &= \sigma\EE\{\bw[n']\bh^{(\ell)}\}\bz_K + \sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\} + o(\sigma^2) \ .
\end{align*}
We remark that
\[
\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\}=\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}\ .
\]
Moreover, using Delta method one can show that we have the asymptotic result:
\begin{equation}
\EE\{\bw[n']\bh^{(\ell)}\} \underset{K\to\infty}{\longrightarrow} 0
\label{eq:cov.ap}
\end{equation}
Finally:
\begin{align*}
\bgamma[n,n'] &\underset{K\to\infty}{\sim} \sigma^2\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)} + o(\sigma^2) \ .
\end{align*}

\paragraph{If $n'\geq N$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing. Then, combining result~\eqref{eq:bias.ap} and equations~\eqref{I-eq:cov01} and~\eqref{eq:cov.ap}, we obtain:
\begin{align*}  
\bgamma[n,n'] &= \bz_K^T\EE\left\{{\balpha^{(\ell)}}^T\balpha^{(\lambda)}\right\}\bz_K + \sigma\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\}\bz_K+ \sigma\EE\{\balpha^{(\lambda)}\bw_K\balpha^{(\ell)}\}\bz_K \\
& +\sigma^2\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\bw_K\}-\bz[n]\bz[n']+o(\sigma^2) \\
&= \bz_K^T\EE\left\{{\bh^{(\ell)}}^T\bh^{(\lambda)}\right\}\bz_K + \balpha_0^{(\ell)}\sigma\EE\{\bw_K\bh^{(\lambda)}\}\bz_K + \sigma\EE\{\bh^{(\ell)}\bw_K\}\bz[n']  \\
&+ \sigma\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\}\bz_K+ \sigma\EE\{\bh^{(\lambda)}\bw_K\}\bz[n] + \sigma\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\}\bz_K \\
& + \sigma\EE\{\bh^{(\lambda)}\bw_K\bh^{(\ell)}\}\bz_K+\sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bh^{(\lambda)}\bw_K\}+\sigma^2\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\bw_K\} \\
&+\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2) \\
&\underset{K\to\infty}{\sim} \dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2)
\end{align*}
The Isserlis' theorem also gives the following result:
\begin{align*}
\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} &= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\bh^{(\lambda)}[m']\bw_K[m']\} \\
&= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\}\EE\{\bh^{(\lambda)}[m']\bw_K[m']\} + \EE\{\bh^{(\ell)}[m]\bw_K[m']\}\EE\{\bh^{(\lambda)}[m']\bw_K[m]\} \\
&\hspace{35pt} + \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m']\}\underbrace{\EE\{\bw_K[m]\bw_K[m']\}}_{=\delta_{m,m'}} \\
&\underset{K\to\infty}{\sim} \sum_{m=0}^{M-1} \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m]\} = \dfrac1K\Tr\left(\bGamma^{(\ell,\lambda)}\right)\ .
\end{align*}
We conclude that:
\begin{align*}  
\bgamma[n,n'] &\underset{K\to\infty}{\sim} \dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\dfrac{\sigma^2}{K}\Tr\left(\bGamma^{(\ell,\lambda)}\right) + o(\sigma^2)\ .
\end{align*}

>>>>

\title{Supplementary material for ``An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects in Time-Frequency Representations''}

@@

%\subsection{Notations}
Recall the model~\eqref{I-eq:model.noise}. Based on the definition of matrices $\bX$ and $\bY$, we have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} := \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$,
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
We call $\bE^{(0)}$ and $\bE^{(1)}$ {\em error matrices} because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
Thus, 
\begin{align*}
\bA_0 :=\bS^{(1)}{\bS^{(0)}}^\inv\,,\quad\tilde\bA := (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\,.
\end{align*}
As a result, for $\ell\in \mathbb{N}$, 
\begin{align}
\nonumber
\bh^{(\ell)} &= \balpha^{(\ell)} - \balpha^{(\ell)}_0 \\
\nonumber
&= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

%\subsection{Study of $\bh^{(\ell)}$}
The randomness of $\bh^{(\ell)}$ completely comes from the error matrices. Besides, notice that the first $M-1$ rows in $\bE^{(1)}$ equal to the last $M-1$ rows of $\bE^{(0)}$. We gather all sources of randomness into an vector $\bg\in\RR^{M(M+1)}$, containing $M$ rows defined as
\[
\bg = \vec\left(
\begin{bmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{bmatrix}
\right)\,,
\]
where "$\vec$" denotes the vectorization operator, concatenating the columns of a given matrix on top of one another. Then, by definition, we have:
\[
\bg = \sigma\bg_1 + \sigma^2\bg_2\ ,
\]
where:
\begin{align*}
\bg_1 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left( \tilde\bz_k\bw_k^T + \tilde\bw_k\bz_k^T \right) \\
\bg_2 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left(\tilde\bw_k\bw_k^T-\tilde\bI \right) \,,
\end{align*}
where $\tilde\bz_k^T= \begin{pmatrix} \bz_k^T & \bz_{k+1}[M-1] \end{pmatrix}$ and $\tilde\bw_k^T= \begin{pmatrix} \bw_k^T & \bw_{k+1}[M-1] \end{pmatrix}$. Then, $\bg_1$ is a Gaussian random vector because it is a linear combination of Gaussian random vectors. Moreover, using the central limit theorem under weak dependence, we can show that $\bg_2$ also converges towards a Gaussian random vector as $K\to\infty$. Combining these two results leads to
\[
\sqrt{K}\ \bg \xrightarrow[K\to\infty]{\cD} \cN(\bzero,\bGamma_0)\ ,
\]
where $\bGamma_0=\EE\left\{\bg\bg^T\right\}$ is a covariance matrix.

Furthermore, one can write $\bh^{(\ell)}$ as $\bh^{(\ell)}=f^{(\ell)}(\bg)$ where $f^{(\ell)}$ is a deterministic function such that:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ . \\
\end{align*}
Then, as $f^{(\ell)}$ is a differentiable function with non-zero differentiation at $0$ {\color{red}[I assume that you have checked all conditions for the delta method. You may consider adding its formula to save the readers' time]}, using the Delta method gives:
\begin{align*}
\sqrt{K}\ \bh^{(\ell)} \xrightarrow[K\to\infty]{\cD} \cN(\bzero,{\bF^{(\ell)}}^T\bGamma_0\bF^{(\ell)})\ ,
\end{align*}
where $\bF^{(\ell)}$ is the Jacobian matrix such that:
\[
\bF^{(\ell)}[m,m'] = \left.\dfrac{\partial f^{(\ell)}_m}{\partial\bg[m']}\right\vert_{\bg=\bzero}\ .
\]

@@

\subsection{Expression of the bias $\bmu$.}
Clearly, $\bmu[n]=0$ when $n\in I$. When $n=N-1+\ell$, we have

@@

Let us first evaluate the expression of $\balpha_0^{(\ell)}\bz_K$. We have

@@

where $\bU[m,m']=\frac1{\sqrt{M}}e^{-2\ii\pi mm'/M}$ and $\bLambda^{(0)} = \mathrm{diag}(\lambda_0^{(0)},\dots,\lambda_{M-1}^{(0)})$ with

@@

Therefore,

@@

{\bS^{(0)}}^\inv  &= \bU{\bLambda^{(0)}}^\inv\bU^*\,,

@@

which leads to

@@

{\bS^{(0)}}^\inv[m,m']  &= \dfrac1{\sigma^2}\delta_{m,m'}-\sum_{j=1}^J\dfrac{\Omega_j^2}{2\sigma^2(\sigma^2+\Omega_j^2M/4)}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,.

@@

Consequently, we have

@@

&= \delta_{m+1,m'} + \sum_{j=1}^J\dfrac{2\Omega_j^2}{\Omega_j^2M+4\sigma^2}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.

@@

Thus,

@@

\end{pmatrix}\,.

@@

By induction, we have

@@

\, .

@@

Then,

@@

&=\sum_{m=0}^{M-\ell}\balpha_0^{(1)}[m]\bz[N-M+\ell+m-1]+\sum_{m=M-\ell+1}^{M-1}\balpha_0^{(1)}[m]\balpha_0^{(m-M+\ell)}\bz_K\,.

@@

But,

@@

By induction from~\eqref{eq:seq}, we have

@@

{\color{red}[if it is possible to get the convergence rate, like $\EE\{\bh^{(\ell)}\}=O(1/K)$, that would be great!]} Consequently,

@@

\frac{1}{\sigma}\bmu[N-1+\ell] = o(1)

@@

when $K\to\infty$.

\subsection{Expression of the covariance $\bgamma$.}
Take $n>N$, and denote $n=N-1+\ell$.  To derive the covariance, let us segregate the cases.

\paragraph{When $n'\in I$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian when $K\to \infty$. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing {\color{red}[there is a gap here. Note that when $K$ is finite, it is approximated by Gaussian but not Gaussian. The discrepancy should be made clear.]}. Then, combining result~\eqref{eq:bias.ap} and equation~\eqref{I-eq:bias0}, we obtain:
\begin{align*}
\bgamma[n,n'] &= \sigma\EE\{\bw[n']\bh^{(\ell)}\}\bz_K + \sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\} + o(\sigma^2) 
\end{align*}
when $K\to \infty$.
We remark that
\[
\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\}=\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}\ .
\]
Moreover, using Delta method one can show that we have the asymptotic result
\begin{equation}
\EE\{\bw[n']\bh^{(\ell)}\} \underset{K\to\infty}{\longrightarrow} 0\,.
\label{eq:cov.ap}
\end{equation}
As a result, we have
\begin{align*}
\bgamma[n,n'] &= \sigma^2\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}+ o(\sigma^2)
\end{align*}
when $K\to\infty$. {\color{red}[Note that $o(\sigma^2)$ becomes $0$ when $K\to \infty$. So use either ``$\bgamma[n,n']= \sigma^2\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}+ o(\sigma^2)$ when $K\to \infty$'' or ``$\bgamma[n,n'] \to \sigma^2\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}$ when $K\to \infty$''.]}

\paragraph{When $n'\geq N$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing. {\color{red}[The same gap here.]} Then, combining equations~\eqref{I-eq:cov01}, \eqref{eq:bias.ap} and~\eqref{eq:cov.ap}, we obtain
\begin{align*}  
\bgamma[n,n'] = &\,\bz_K^T\EE\left\{{\balpha^{(\ell)}}^T\balpha^{(\lambda)}\right\}\bz_K + \sigma\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\}\bz_K+ \sigma\EE\{\balpha^{(\lambda)}\bw_K\balpha^{(\ell)}\}\bz_K \\
& +\sigma^2\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\bw_K\}-\bz[n]\bz[n']+o(\sigma^2) \\
= &\,\bz_K^T\EE\left\{{\bh^{(\ell)}}^T\bh^{(\lambda)}\right\}\bz_K + \balpha_0^{(\ell)}\sigma\EE\{\bw_K\bh^{(\lambda)}\}\bz_K + \sigma\EE\{\bh^{(\ell)}\bw_K\}\bz[n']  \\
&+ \sigma\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\}\bz_K+ \sigma\EE\{\bh^{(\lambda)}\bw_K\}\bz[n] + \sigma\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\}\bz_K \\
& + \sigma\EE\{\bh^{(\lambda)}\bw_K\bh^{(\ell)}\}\bz_K+\sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bh^{(\lambda)}\bw_K\}+\sigma^2\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\bw_K\} \\
&+\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2) \\
= &\,{\color{blue}\dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K} +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2)
\end{align*}
when $K\to\infty$ {\color{red}[in the last equation, make clear which term depends on which equation \eqref{I-eq:cov01}, \eqref{eq:bias.ap} and~\eqref{eq:cov.ap}.] [The previous or current asymptotic expressions with $\dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K$ are both not ideal. Either using your previous notation or following what I prefer here, the behavior of $\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K$ should be made clear. Is it bounded? If it is bounded, then use $=O(1/K)$ to replace $\to \dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K$. If not, how does it depend on $K$ should be made clear.] [Moreover, if you prefer to use your previous notation, you may clarify what it means by $\sim$.]}.
The Isserlis' theorem also gives the following result {\color{red}[the same gap here.]}
\begin{align*}
\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} &= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\bh^{(\lambda)}[m']\bw_K[m']\} \\
&= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\}\EE\{\bh^{(\lambda)}[m']\bw_K[m']\} + \EE\{\bh^{(\ell)}[m]\bw_K[m']\}\EE\{\bh^{(\lambda)}[m']\bw_K[m]\} \\
&\hspace{35pt} + \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m']\}\underbrace{\EE\{\bw_K[m]\bw_K[m']\}}_{=\delta_{m,m'}} \\
&\to \sum_{m=0}^{M-1} \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m]\} = \dfrac1K\Tr\left(\bGamma^{(\ell,\lambda)}\right)
\end{align*}
when $K\to \infty$.
We thus conclude that
\begin{align*}  
\bgamma[n,n'] &\to {\color{blue}\dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K} +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\dfrac{\sigma^2}{K}\Tr\left(\bGamma^{(\ell,\lambda)}\right) + o(\sigma^2)
\end{align*}
when $K\to \infty$.
